\section{Work Experience}
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{
		\textbf{Software Architect (R\&D)}
			\hfill
			{Sep. 2018 --- \phantom{XXX. 0000}}
		}
	\smallbreak
	%\smallskip
	\parbox{\linewidth}{Dolphin Interconnect Solutions}
	\smallskip
	\smallskip
}
\parbox[t][][t]{\linewidth}{
	{\parbox{\linewidth}{
		\parbox{\linewidth}{
			\textbf{PhD Student}
			\hfill
			{Feb. 2015 --- Sep. 2018}
		}
	}}
	\smallbreak
	\parbox{\linewidth}{Simula Research Laboratory}

%	\parbox{\linewidth}{\textbf{Software Architect}
%		\hfill {{Sep. 2018 --- \phantom{XXX. 0000}}}}
%		\smallbreak
%	\parbox{\linewidth}{Dolphin Interconnect Solutions}
%	\smallbreak
%	\parbox{\linewidth}{\textbf{PhD Student}
%		\hfill {{Feb. 2015 --- \phantom{Jun. 2019}}}}
%		\smallbreak
%	\parbox{\linewidth}{Simula Research Laboratory\\and University of Oslo}
	
	\bigskip
	Developed a framework for high-performance, distributed I/O, resource sharing,
	and composable architectures in PCIe clusters in collaboration with Dolphin Interconnect Solutions.
	Gained experience with PCIe, NTBs, high-speed interconnects, RDMA, distributed shared-memory
	architectures, NVMe, GPU programming, Nvidia GPUDirect, driver development and low-level kernel hacking.
%	Worked on a framework for distributed high-performance IO in a PCIe cluster in
%	collaboration with Dolphin Interconnect Solutions. 
%	Gained
%	experience with PCIe, NTBs, high-speed interconnects, RDMA, memory
%	architectures, NVMe, GPU programming, and driver development for Linux.

	\bigskip
	\begin{itemize}
		\item{Implemented Linux KVM hypervisor support using VFIO mediated device drivers
			for passing through physically remote devices to a local VM.}\\[-.6em]
		\item{Contributed to the design, development and testing of the SmartIO
			extension to the SISCI shared-memory API.}\\[-.6em]
%		\item{Created a library for developing distributed storage
%			applications using SmartIO extension to SISCI.
%			As proof of concept, I used this library in a CUDA program to demonstrate direct
%			IO between GPUs and NVMe disks a cluster without
%			involving CPU in the data path.}\\[-.6em]
		\item{Created a software library and userspace NVMe driver 
			for developing distributed storage applications using SmartIO.
			Demonstrated concurrent, zero-copy and direct block-level access to NVMe drives from
			multiple GPUs in the cluster without involving CPU in the data path.}\\[-.6em]
		\item{Investigated performance issue with Intel IOMMUs and
			implemented support for PCIe peer-to-peer transfers for SmartIO devices.}\\[-.6em]
		\item{Developed various RDMA performance benchmarking tools.}
	\end{itemize}
	\bigskip
	\bigskip
}

\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{
		\textbf{Software Developer}
		\hfill {{Aug. 2014 --- Feb. 2015}}
	}
	\smallbreak
	\parbox{\linewidth}{Bridge Technologies}

	\bigskip
%	Worked at a company that made hardware and software
%	for real-time analysis of IPTV and OTT digital video and network
%	traffic. Got experience with video encoding, PIM-SM multicasting, MPEG transport
%	streams, working with C++ in an embedded environment, and
%	network traffic analysis.

	Gained experience with analysing IPTV and OTT digital video, network traffic analysis,
	PIM-SM multicasting, and working with embedded C++.
%	Implemented an MPEG-4/AVC video stream parser in order to extract and
%			validate CEA608/708 closed captioning data and provide real-time notifications.

	\bigskip
	\begin{itemize}
		\item{Implemented a real-time MPEG transport stream parser for the VB288 content extractor using libpcap for live capturing
			multicast IPTV video.}\\[-.6em]
		\item{Implemented parser for MPEG-2 and MPEG-4/AVC video streams in order to extract and
			validate CEA608/708 closed captioning data and provide real-time event notifications.}

%		\item{Implemented a MPEG-2 and MPEG-4/AVC video stream parser for the
%			VB288 content extractor using libpcap for live network
%			traffic capturing.}\\[-.6em]
%		\item{Made a validator for CEA608/708 closed captioning data
%		embedded into MPEG-2 and MPEG-4 video streams with real-time
%			error notifications.}
	\end{itemize}
	\bigskip
	\bigskip
}


%%% Full time. Feb. 2013 -- Aug. 2014
%%% Part time Mar 2011 -- Jun 2012
\parbox[t][][t]{\linewidth}{
	{\hfill\parbox{\linewidth}{
		\parbox{\linewidth}{
			\textbf{Software Development Engineer}
			\hfill
			{Feb. 2013 --- Aug. 2014}
		}
	}}
	\smallskip
	\parbox{\linewidth}{Fotoware}

	\bigskip
	Worked mainly with the back-end of FotoWeb, a web-based image and video
	archiving system with full-text metadata search and workflows based on
	metadata tags. Gained experience working with Apache2, MongoDB, web
	caches, designing REST services from the ground up, and creating HTTP endpoints with C++ (FastCGI)
	and Python (Flask / mod\_wsgi).

	\bigskip
	\begin{itemize}
		\item{Implemented a hierarchical metadata taxonomy tree that
			supported CRUD operations and assignment to assets of tens of thousands of metadata tags within
			milliseconds.}\\[-.6em]
		\item{Created a configurable workflow engine allowing users to
			create custom pipelines and workloads for processing assets based on
			metadata tags.}\\[-.6em]
		\item{Made a background job scheduler with support for
			webhooks and asynchronous message-passing as well as
			bulk file operations.}\\[-.6em]
		\item{Implemented both back-end and front-end for exporting
			assets to an external CMS and an access 
			management UI for these exports.}\\[-.6em]
		%\item{Contributed to migrating the existing code base from IIS to Apache.}
	\end{itemize}
}
