\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[firstyear=2004,lastyear=2019]{moderntimeline}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[a4paper,bottom=0.8in,top=0.8in,right=1.05in,left=1.05in]{geometry}
\usepackage{lastpage}

\firstname{Jonas}
\lastname{Markussen}

% Below is for casual colors
%\patchcmd{\makecvtitle}{\color{color2!50}\@firstname}{\color{color2}\@firstname}{}{}
%\patchcmd{\makecvtitle}{\color{color2}\@lastname}{\color{color2}\@lastname}{}{}

\title{}
%\photo[75pt][0.05pt]{jonas3}
\email{jonassm@ifi.uio.no}
%\mobile{+47 408 62 630}
\social[linkedin]{jonasmarkussen}
\social[github]{enfiskutensykkel}
%\social[twitter]{1fiskutensykkel}

%\homepage{folk.uio.no/jonassm}

%\rfoot{\color{gray}\textit{\thepage/\pageref{LastPage}}}
%\setlength{\hintscolumnwidth}{2.7cm}
%\setlength{\hintscolumnwidth}{2.3cm} % use this with tl
\setlength{\hintscolumnwidth}{2.1cm}
%\tltextstart[base east]{\scriptsize}
%\tltextend[north west]{\scriptsize}
%\newcommand{\h}[1]{\textbf{{#1}}}
\newcommand{\hdate}[2]{\textit{{#1} -- {#2}}\\}

\AfterPreamble{\hypersetup{
	pdfauthor={Jonas Markussen},
	pdftitle={Jonas Markussen},
	pdfsubject={CV for Jonas Markussen}
}}

\begin{document}
\makecvtitle

\vspace{-.5em}
\section{Summary}
PhD student currently involved in the Unified PCIe IO project at Simula Research Laboratory.
Experience with programming in C, especially for Linux kernel hacking.
Knowledgable about IP networking and the Linux kernel TCP implementation.
Mainly interested in systems- and embedded programming, specifically performance optimisations,
distributed systems and low-level network programming.
I also have some experience with GPU programming (CUDA) and GPU workloads. 
Some web back-end experience with C++ (Apache+FastCGI) and Python (mod\_wsgi/flask).
%I'm a PhD student currently involved in the Unified PCIe IO project at Simula Research La/
%I have a passion for systems- and embedded programming, and I'm interested in
%distributed systems and low-level computer communication. During my education, I've
%gained experience with Linux kernel development as well as driver programming.
%From working in the industry, I have experience with back-end development in C++
%and Python as well as software engineering in general.
\vspace{.3em}

%\section{Professional experience}
\section{Experience}
%\tlcventry[orange]{2015}{0}{PhD student}{Simula Research Laboratory AS}{}{}{
\cventry{2015 -- \phantom{2018}}{PhD student}{Simula Research Laboratory}{}{}{
%\hdate{02.2015}{Present}
\hdate{February 2015}{Present}
Working on a software framework for allowing time-sharing and dynamic virtual migration of IO devices, such as GPUs and SSDs, 
between multiple hosts connected in a PCIe cluster, without requiring any changes to device drivers or
applications. This involves working with PCIe NTB-based interconnects and Linux kernel module programming.
I am also currently involved in trying to accellerate a 3D reconstruction tool using CUDA and running
it on a PCIe cluster as a proof-of-concept workload for this framework. \\
}

%\tlcventry[olive]{2014}{2015}{Software developer}{Bridge Technologies Co AS}{}{}{
\cventry{2014 -- 2015}{Software developer}{Bridge Technologies Co AS}{}{}{
%\hdate{08.2014}{02.2015}
\hdate{August 2014}{January 2015}
C++ programmer at Bridge Tech., a company that creates digital monitoring devices and network probes.
Worked with VB288, which is a server product that joins a PIM-SM multicast group
and extracts content from MPEG-2 transport streams in order to run some analysis.
I was involved in a project to extract and inspect
CEA608/708 closed captioning data embedded into the user data of MPEG-2 and MPEG-4 AVC video streams.
Gained experience with MPEG transport streams and video streams, as well as streaming over IP multicast.\\
}

%\tlcventry{2011}{2014}{Software development engineer}{Fotoware AS}{}{}{
\cventry{2011 -- 2014}{Software development engineer}{Fotoware AS}{}{}{
%\hdate{03.2011}{07.2014}
\hdate{March 2011}{July 2014}
C++ and Python programmer at Fotoware, a company that develops digital asset management solutions.
Worked mainly with the back-end of FotoWeb, which is an web-based image archiving system
with full-text metadata search and workflows based on XMP/IPTC metadata.
Created the back-end for various REST services such as user-configurable workflows,
a global webhook queue, hierarchical metadata taxonomy support and a CMS export tool.
I was also involved in migrating the platform from IIS to Apache.\\
}

%\tlcventry[purple]{2010}{2011}{Part-time programmer}{Redimi AS}{}{}{
\cventry{2010 -- 2011}{Part-time programmer}{Redimi AS}{}{}{
%%\hdate{09.2010}{02.2011}
\hdate{August 2010}{January 2011}
Worked 15-20 hours per week as a Java developer next to my studies. The company made
server monitoring solutions, and I was involved with maintaining and development of their
database monitoring application before it was discontinued. 
%%%As the sole programmer at the time, I got experience with most
%%%areas of software development.
}

%\tlcventry[brown]{2009}{2011}{Teaching assistant}{Department of Informatics, UiO}{}{}{
%\hdate{09.2009}{06.2011}
%\begin{itemize}
%\item{Home exam corrector in the course \emph{INF3190 Computer communication}}
%\item{Teaching assistant in the course \emph{INF3151/4151 Operating systems}}
%\item{Computer lab assistant in the course \emph{INF3190 Computer communication}}
%\item{Computer lab assistant in the course \emph{INF1060 Introduction to operating systems}}
%\end{itemize}
%}

\section{Education}
%\tlcventry[orange]{2015}{0}{PhD, Informatics}{University of Oslo}{}{}{
%\hdate{02.2015}{2018 (Expected)}
%Doctoral degree in computer science. I'm doing my research at Simula.
%}
%\tlcventry[brown]{2010}{2014}{MSc, Informatics}{University of Oslo}{}{}{
\cventry{2010 -- 2014}{MSc, Informatics}{University of Oslo}{}{}{
%\hdate{09.2010}{09.2014}
Graduate degree in computer science. My master thesis was on evaluating various latency-reducing modifications to the TCP retransmission algorithm in the Linux kernel.\\
}
%\tlcventry[violet]{2006}{2010}{BSc, Informatics}{University of Oslo}{}{}{
\cventry{2006 -- 2010}{BSc, Informatics}{University of Oslo}{}{}{
%\hdate{09.2006}{06.2010}
Undergraduate degree in computer science. For my bachelor project we implemented an OS kernel for x86/i486 in the course {INF3151} Operating Systems.}

%\section{Selected Publications}
%\cvline{2016}{\textit{Device Lending in {PCI} Express Networks}, \scriptsize{Proceedings of the 26th International Workshop on Network and Operating Systems Support for Digital Audio and Video (NOSSDAV), Klagenfurt, Austria}}
%\cvline{2015}{\textit{Latency and Fairness Trade-Off for Thin Streams using Redundant Data Bundling in TCP}, \scriptsize{IEEE 40th Conference on Local Computer Networks (LCN), Clearwater Beach, Florida, USA}}
% Note to future self: only include first author articles
%\section{Publications}
%\cvline{2016}{\textit{Device Lending in {PCI} Networks}, ACM NOSSDAV '16}
%\cvline{2015}{\textit{Latency and Fairness Trade-Off for Thin Streams using Redundant Data Bundling in
%TCP}, IEEE LCN '15}

%\section{Skills and knowledge}
%\cvdoubleitem{a}{b}{c}{d}
%\section{Skills and knowledge}
%\cvline{\h{Development}}{Modelling and design; test-driven development; debugging; object-oriented programming; algorithms and data structures; development methods}
%\cvline{\h{Web}}{HTTP; FastCGI; Apache with mod\_wsgi; MongoDB; PostgreSQL; SEO; web caching, reverse proxies; RESTful API design; AJAX; HTML5/CSS3; Flask}
%\cvline{\h{Networking}}{Internet architecture; TCP; TCP/IP protocol stack; IPv4; IPv6; mobile IP; MANET; WiFi/802.11 protocol family; QOS; AQM; multicast (PIM-SM/DM); congestion control; routing algorithms; SCTP; network components}
%\cvline{\h{Architecture}}{Linux kernel; low-level and asynchronous programming; x86 architecture; multi-threading; driver/kernel module programming; digital circuit design; multi-core architectures; GPU programming (CUDA); run-time optimisations; Atmel microcontrollers; programmable logic (FPGA); SIMD; PCI express}
%\cvline{\h{Languages}}{GNU C and C99/C11; C++11 with Boost; Python 2.7; JavaScript with jQuery; VHDL; Java 7; PHP 5; Bash; SQL; GAS assembly (IA-32/x86-64)}

%\section{References}
%Complete work history, publication list, as well as work references are available upon request.

\end{document}
